SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs

### 2021-01-29 maintex.tex
updated paper for second revision

\begin{abstract}
We compare the radial profiles of the specific star formation rate (sSFR) in a sample of \textbf{169} star-forming galaxies in close pairs with those of mass-matched \textbf{control} galaxies in the SDSS-IV MaNGA survey. We find that the sSFR is centrally enhanced (within one effective radius) in interacting galaxies by $\sim$0.3 dex and that there is a weak sSFR suppression in the outskirts of the galaxies of $\sim$0.1 dex. We stack the differences profiles for galaxies in five stellar mass bins between \logm\ $=$ 9.0$-$11.5 and find that the sSFR enhancement has no dependence on the stellar mass. The same result is obtained when the comparison galaxies are matched to each paired galaxy in both stellar mass and redshift. In addition, we find that that the sSFR enhancement is elevated in pairs with nearly equal masses and closer projected separations, in agreement with previous work based on single-fiber spectroscopy. We also find that the sSFR offsets in the outskirts of the paired galaxies are dependent on whether the galaxy is the more massive or less massive companion in the pair. The more massive companion experiences zero to a positive sSFR enhancement while the less massive companion experiences sSFR suppression in their outskirts. \textbf{Our results illustrate the complex tidal effects on star formation in closely paired galaxies. }
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{bpt-cmd.pdf}
\caption[]{(\textbf{Left}) Color-magnitude diagram for MaNGA galaxies. \textbf{(\textbf{Center}) BPT diagram for the MaNGA galaxies. (\textbf{Right}) The WHAN diagram for the MaNGA galaxies.} The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top. The {\it purple} diamonds represent the paired galaxies which are classified as retired (by the \ewha\ cut), the {\it blue} diamonds represent the star forming paired galaxies (by the BPT diagram), the {\it green} diamonds represent the composite star forming-AGN paired galaxies (by the BPT diagram), and the {\it Red} diamonds represent the paired galaxies containing an AGN (by the BPT diagram).}
\label{fig:cmd}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

{\bf 
We use {\sc spfit} to model the MaNGA datacubes. The IDL package is publicly available\footnote{\url{https://github.com/fuhaiastro/spfit}} and was first used in our previous study of close galaxy pairs in MaNGA \citepalias{Fu:2018}. While data products from the MaNGA Data Analysis Pipeline \citep[DAP;][]{Belfiore:2019} and {\sc pipe3d} \citep{Sanchez:2016a, Sanchez:2016b} are available, {\sc spfit} allows us to combine spectra inside a given aperture before fitting the combined spectrum. The feature alone made it better suited for this project. Additional features of {\sc spfit} include: (1) simultaneously fitting emission lines and stellar continuum, (2) coadding spaxels with either a Voronoi tessellation or arbitrary polygons while accounting for covariances, (3) modeling asymmetric emission lines, broad AGN emission lines, AGN continuum, and various dust-extinction laws, and (4) utilizing multi-threading when processing a large number of datacubes.

@@

For model optimization, we prefer a fast algorithm like the Levenberg-Marquardt nonlinear least-squares minimization algorithm implemented in {\sc mpfit} \citep{Markwardt:2009}. But for complex spectral models like ours, the success of the fitting routine relies on a good initial ``guess'' solution, which can be provided by the penalized pixel-fitting method \citep[pPXF;][]{Cappellari:2017}. The pPXF method is robust because it solves the weights of the templates with a linear algorithm \citep{Lawson:1974} {\it independently} from solving the Gauss-Hermite LOSVD with a nonlinear optimizer ({\sc mpfit}). The {\sc spfit} package implements a three-stage fitting procedure: First, it masks out spectral regions around emission lines from the input spectrum and use pPXF on the masked spectrum with SSP-only templates to obtain the initial ``best-fit'' parameters of the stellar continuum; Then, it subtracts the best-fit stellar continuum model from the spectrum and use pPXF to fit the residual emission-line-only spectrum with Gaussian emission-line templates to obtain the initial ``best-fit'' parameters of the emission lines; Finally, it uses {\sc mpfit} on the full input spectrum with the two sets of ``best-fit'' parameters from pPXF to simultaneously fit all of the parameters describing the emission lines and the stellar continuum. Saved in the final FITS file are the best-fit parameters and their uncertainties, including emission-line fluxes, equivalent widths, and kinematics and luminosity-weighted stellar masses, ages, metallicities, and kinematics. 
}

@@

\textbf{Based on the WHAN diagram, shown in the right panel of Figure \ref{fig:cmd}, we apply an \ewha\ $\ge$ \textbf{6\AA} cut on galaxy spectra extracted from a 1.0~\reff\ aperture to ensure that all \textbf{retired} galaxies are removed from the sample \citep{Cid-Fernandes:2011}.}

@@

\textbf{Broad-line AGN comprise $\sim$0.9\% of MaNGA's galaxy sample where \citet{Lacerda:2020} found a fraction of $\sim$2.8\% from the CALIFA survey and \citet{Sanchez:2018} found a fraction of $\sim$1.33\% from the MaNGA's MPL-5 sample (which observed $\sim$2700 galaxies).  
}

{\bf Among the 6142 MaNGA IFUs considered here, 404 cover close galaxy pairs and multiples. The sample includes 327 pairs, 67 triplets, 7 quadruplets, and 1 quintuplet. Table\,\ref{tab:sample} lists the coordinates and redshifts of these galaxy components in pairs/multiples.} When a MaNGA target has multiple companions galaxies, we chose the closest companion to define the pair's mass ratio and projected separation.

For this study, we further restrict the sample by setting a relative velocity cut of $\Delta v$ $<$ 500 km s$^{-1}$. Given the redshift range of the MaNGA sample and the size of MaNGA's IFUs, the maximum projected separation for a companion galaxy in the IFU is $\sim$40 kpc. Again, the galaxy sample is also restricted to galaxies with a stellar mass range of \logm\ $=$ 9.0$-$11.5 and galaxies in the Primary or Secondary MaNGA subsamples. We also require that the galaxies are classified as star forming as described in \S~\ref{sec:data}. These requirements reduce our sample down to 54 star forming MaNGA targets with inside-IFU companions. \textbf{While we use the identified companions to select galaxy pairs, we only build radial profiles for the MaNGA target galaxies. We do this because the identified companions are not included in the NSA catalog which we use to build the radial profiles for the galaxies.}

@@

To show how the population of galaxy pairs differs from isolated galaxies, we will compare our pair sample to a sample of \textbf{control} galaxies in the MaNGA survey. We build this control sample from the MaNGA target galaxies which have no spectroscopic companions within $r_{\rm p}$ $<$ 50 kpc and $\Delta v$ $<$ 500 km s$^{-1}$ either inside or outside of the IFU. This gives us a control sample of 1830 star forming control galaxies.

It has been shown that the SFR in galaxies is dependent on both the stellar mass and the redshift of the galaxies \citep[e.g.,][]{Noeske:2007}. We will compare our interacting galaxies with \textbf{control} galaxies of a similar stellar mass, redshift, and radial size, to account for these other dependencies. To do this, we will use two different methods of pair - control comparison.

@@

In the second method, we select a ``tailored'' control sample for each paired galaxy from the full sample of isolated galaxies. We select a subsample of 20 control galaxies for each paired galaxy. We first select all of the control galaxies which are within 0.1 dex in stellar mass, \textbf{0.025 in redshift, 20\% in effective radii}, and within the same MaNGA subsample (e.g. Primary or Secondary) as the paired galaxy. With these requirements, most paired galaxies will find between 20$-$60 control galaxies. Since we want each paired galaxy to be treated in a similar manner, we randomly down-select the total number of acquired control galaxies to 20. A given control galaxy may be selected for multiple pairs by the pipeline; most of the control galaxies are used at least once and the average number of times a given control is reused is between 2$-$4 times. In the cases where a paired galaxy does not initially acquire 20 control galaxies we iteratively expand the stellar mass limit by 0.1 dex, the redshift by 0.025, and the \reff\ by 5\% until at least 20 control galaxies are found. \textbf{39 pairs required 1 extra iteration, 15 pairs required 2 extra iterations, 5 pairs required 3 extra iterations, and 2 pairs required 4 extra iterations. }

@@

\subsection{Specific Star Formation Rate}
\textbf{We calculate the star formation rates in the pair and control galaxies with the emission lines extracted with our spectra fitting code, {\sc spfit} (described in Section \ref{sec:spfit}).} We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}. The extinction is parameterized as $R_V$ $\equiv$ $A_V/E(B-V)$ $=$ 3.1, where we estimate the value of the $V$-band extinction, $A_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for Case-B recombination.

@@

\textbf{
We check our measurement of the specific star formation rate with the equivalent width of the H$\alpha$ line, \ewha, since it is a known proxy for the sSFR. This is useful as the sSFR is dependent on {\sc spfit}'s measurement of the stellar mass while \ewha\ is an observable. As we will show in Section \ref{sec:results}, the radial profiles of \ewha\ is consistent with radial profiles of the sSFR.
}

\textbf{
The signal to noise ratio of the data will decrease with wide galactocentric radii. MaNGA is designed to cover 1.5 \reff\ for galaxies in the Primary sample and 2.5 \reff\ in the secondary sample. These are not hard limits, data will exist beyond these radii, especially along the semi-minor axis of galaxy; however, the data beyond these limits may be unreliable due to low signal to noise. To control the quality of the used data, we only use spaxels with S/N $\ge$ 3 for the H$\alpha$ line. We also restrict the used spaxels to those with \ewha\ $\ge$ 6 \AA\ to remove retired regions from the survey \citep{Cid-Fernandes:2011}, which effectively sets -10.8 yr$^{-1}$ as the lower limit to the sSFR in our galaxies.
}

@@

We fit the geometry with apertures from both catalogs when available. When using the first method of pair-control comparison, where pairs and controls are grouped into stellar mass bins, we fit the control galaxies with the NSA apertures. When making the comparison with the second method, paired galaxies fitted with the NSA apertures are compared against controls fitted with the NSA apertures and paired galaxies fitted with the \citet{Simard:2011} apertures are compared against controls fitted with the \citet{Simard:2011} apertures. Further, when defining a galaxy's geometry with the \citet{Simard:2011} apertures we also use the masses given in the catalog for the total stellar mass of the galaxy. Note that although we carefully treat the two catalogs separately whenever possible, we find excellent agreement in the geometry parameters of \textbf{control} galaxies in both catalogs.

@@

\textbf{The MaNGA sample does not have a uniform spatial coverage, 63\% of the sample is designed to cover 1.5 \reff\ (the Primary+ subsample) and 37\% of the sample is designed to cover 2.5 \reff\ (the Secondary subsample). This means that there will be fewer selected spaxel beyond 1.5 \reff\ and the S/N of the selected spaxels will be lower than those within 1.5 \reff. We decide to still extend our radial profiles out to 2.5 \reff, but emphasize that the data beyond 1.5 \reff\ is lower in quality. }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{ssfr_comb.pdf}
\caption[]{The log(sSFR) as a function of galactocentric radius for control galaxies (\textbf{Left}) and galaxy pairs (\textbf{Middle}). The difference between the profiles of the paired galaxies and the control galaxies are shown in the \textbf{Right} panel. The dashed black profile represents the mean of the difference profiles. The colors of the profiles represent the mass range of the selected galaxies which is given in the legend along with the number of galaxies in that mass bin in parantheses. The highlighted region around the profiles represent the standard error of the mean of the data at the given radius interval. }
\label{fig:ssfr_prof}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In the first method, paired and control galaxies are grouped into five evenly spaced stellar mass bins between \logm\ $=$ 9.0$-$11.5. Within each stellar mass bin, we create a median profile of log(sSFR) as a function of \reff-scaled galactocentric distance for both paired and control galaxies. The control profiles are constructed using all available control galaxies within each mass bin. The error associated with the ``stacked'' profile is the standard error of mean of the data at each radius bin. \textbf{Here we define the standard error of the mean, $\sigma_{\overline{x}}$, as,
\begin{equation}
\sigma_{\overline{x}} = \frac{\sigma}{\sqrt{n}},
\end{equation}
where $\sigma$ is the standard deviation and $n$ is the sample size.}

@@

\textbf{ 
We repeat this analysis for the \ewha\ in Figure \ref{fig:ewha_prof}. We find that the \ewha\ profiles are in close agreement with the sSFR profiles, which shows that we can be confident of {\sc spfit}'s measurement of the sSFR. We do see that the pair-control offsets are lightly suppressed using the \ewha\ as the $\Delta$log(\ewha) is only enhanced by 0.25 dex where the $\Delta$log(sSFR) was enhanced by 0.30 dex. 
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=0.8\linewidth]{ssfr_mass.pdf}
\caption[]{The \textbf{Left} panel shows the $\Delta$log(sSFR) profiles where the difference profiles are constructed from the difference between the paired galaxy profiles and a set of 20 control galaxies. The profiles are split into five different stellar mass bins and the highlighted region about the profiles represent the standard error of mean of the profile. The black dashed line represents the mean profile between the four difference mass ranges. The number of paired galaxies in each mass range is given in the legend in parentheses. The \textbf{Right} panel shows the nuclear $\Delta$log(sSFR) \textbf{extracted from a 0.5\reff\ aperture}. The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars). The vertical error bars on the black squares represent the standard deviation within the bin. The horizontal, dashed black line represents the median central enhancement of the pair sample. Galaxies in the outside-IFU (Blue) and inside-IFU (Red) samples are separately depicted.
}
\label{fig:ssfr_mass}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{Tailored-Controls Difference Profiles}\label{sec:tailored}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=0.8\linewidth]{ssfr_dm.pdf}
\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by the mass ratio of the pair. The \textbf{top} row is the absolute value of the mass ratio and the \textbf{bottom} row is the mass ratio without taking the absolute value. Taking the mass ratio without the absolute value allows us to separately study the more massive companions of pairs from the less massive companions from pairs. The inside-IFU sample is left out of this analysis because we do not yet have reliable measurements of their total stellar mass ratios.}
\label{fig:ssfr_dm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the second method, we match each paired galaxy to a set of 20 control galaxies of similar stellar masses and redshifts, as described in \S~\ref{sec:control}. We then take the median of the azimuthally averaged profiles of the tailored control sample. Finally, we obtain the $\Delta\log$sSFR profile for each of the \textbf{169} paired galaxies by calculating the difference between its sSFR profile and the median profile of its control sample.

@@

\textbf{To focus on the sSFR offsets in the centers of the galaxies, we also calculate the sSFR difference between each paired galaxy and its control sample within the central 0.5~\reff. The central sSFR is calculated for each galaxy by taking spaxels within 0.5 \reff\ and whose H$\alpha$ flux has S/N $\ge$ 3 and then taking the median value of sSFR of the selected spaxels. Once this is done we calculate the $\Delta$log(sSFR) using the same method as the $\Delta$log(sSFR) radial profiles are made. The central sSFR of a paired galaxy is compared against the sSFR of a set of 20 similar control galaxies, the same set of controls which were used for the $\Delta$log(sSFR) profiles, by taking the difference between the central sSFR of the paired galaxy and the median sSFR of the 20 selected control galaxies. We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}.}

@@

The central enhancement to the sSFR falls to zero around 1.2 \reff\ and the outskirts of the galaxies are lightly suppressed by 0.0$-$0.1 dex. \textbf{Within individual mass ranges, there are some mass ranges which feature large enhancements to the sSFR at large radii while other mass ranges show a strong suppression to the sSFR. There appears to be no dependence on the stellar mass of the pair but, as we will show in the next section, \S~\ref{sec:dm}, these offsets at large radii may be dependent on the mass ratio between the galaxy pairs.}

\textbf{To understand why the profiles of high mass galaxies behave differently from the rest of the sample in Figures \ref{fig:ssfr_prof}, \ref{fig:ewha_prof}, and \ref{fig:ssfr_mass}, we compare the distribution of the projected separation for the whole sample and for galaxies in the highest mass bin in Figure \ref{fig:sep_hist}.} The whole sample has a v-shaped separation distribution. This is the result of the combination of the two different samples, the inside-IFU and outside-IFU samples. The outside-IFU sample should find more pairs at wide projected separations due to the larger volume to find companions in. The separation distribution of the inside-IFU sample is limited by MaNGA's IFU sizes and the sample's redshift distribution; the maximum possible projected separation for a MaNGA target with $z$ $=$ 0.15 and a 127 spaxel IFU is about 40 kpc.

>>>>

\begin{abstract}
We compare the radial profiles of the specific star formation rate (sSFR) in a sample of 169 star-forming galaxies in close pairs with those of mass-matched control galaxies in the SDSS-IV MaNGA survey. We find that the sSFR is centrally enhanced (within one effective radius) in interacting galaxies by $\sim$0.3 dex and that there is a weak sSFR suppression in the outskirts of the galaxies of $\sim$0.1 dex. We stack the differences profiles for galaxies in five stellar mass bins between \logm\ $=$ 9.0$-$11.5 and find that the sSFR enhancement has no dependence on the stellar mass. The same result is obtained when the comparison galaxies are matched to each paired galaxy in both stellar mass and redshift. In addition, we find that that the sSFR enhancement is elevated in pairs with nearly equal masses and closer projected separations, in agreement with previous work based on single-fiber spectroscopy. We also find that the sSFR offsets in the outskirts of the paired galaxies are dependent on whether the galaxy is the more massive or less massive companion in the pair. The more massive companion experiences zero to a positive sSFR enhancement while the less massive companion experiences sSFR suppression in their outskirts. Our results illustrate the complex tidal effects on star formation in closely paired galaxies.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{bpt-cmd.pdf}
\caption[]{(\textbf{Left}) Color-magnitude diagram for MaNGA galaxies. (\textbf{Center}) BPT diagram for the MaNGA galaxies. (\textbf{Right}) The WHAN diagram for the MaNGA galaxies. The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top. The {\it purple} diamonds represent the paired galaxies which are classified as retired (by the \ewha\ cut), the {\it blue} diamonds represent the star forming paired galaxies (by the BPT diagram), the {\it green} diamonds represent the composite star forming-AGN paired galaxies (by the BPT diagram), and the {\it Red} diamonds represent the paired galaxies containing an AGN (by the BPT diagram).}
\label{fig:cmd}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We use {\sc spfit} to model the MaNGA datacubes. The IDL package is publicly available\footnote{\url{https://github.com/fuhaiastro/spfit}} and was first used in our previous study of close galaxy pairs in MaNGA \citepalias{Fu:2018}. While data products from the MaNGA Data Analysis Pipeline \citep[DAP;][]{Belfiore:2019} and {\sc pipe3d} \citep{Sanchez:2016a, Sanchez:2016b} are available, {\sc spfit} allows us to combine spectra inside a given aperture before fitting the combined spectrum. The feature alone made it better suited for this project. Additional features of {\sc spfit} include: (1) simultaneously fitting emission lines and stellar continuum, (2) coadding spaxels with either a Voronoi tessellation or arbitrary polygons while accounting for covariances, (3) modeling asymmetric emission lines, broad AGN emission lines, AGN continuum, and various dust-extinction laws, and (4) utilizing multi-threading when processing a large number of datacubes.

@@

For model optimization, we prefer a fast algorithm like the Levenberg-Marquardt nonlinear least-squares minimization algorithm implemented in {\sc mpfit} \citep{Markwardt:2009}. But for complex spectral models like ours, the success of the fitting routine relies on a good initial ``guess'' solution, which can be provided by the penalized pixel-fitting method \citep[pPXF;][]{Cappellari:2017}. The pPXF method is robust because it solves the weights of the templates with a linear algorithm \citep{Lawson:1974} {\it independently} from solving the Gauss-Hermite LOSVD with a nonlinear optimizer ({\sc mpfit}). The {\sc spfit} package implements a three-stage fitting procedure: First, it masks out spectral regions around emission lines from the input spectrum and use pPXF on the masked spectrum with SSP-only templates to obtain the initial ``best-fit'' parameters of the stellar continuum; Then, it subtracts the best-fit stellar continuum model from the spectrum and use pPXF to fit the residual emission-line-only spectrum with Gaussian emission-line templates to obtain the initial ``best-fit'' parameters of the emission lines; Finally, it uses {\sc mpfit} on the full input spectrum with the two sets of ``best-fit'' parameters from pPXF to simultaneously fit all of the parameters describing the emission lines and the stellar continuum. Saved in the final FITS file are the best-fit parameters and their uncertainties, including emission-line fluxes, equivalent widths, and kinematics and luminosity-weighted stellar masses, ages, metallicities, and kinematics.

@@

Based on the WHAN diagram, shown in the right panel of Figure \ref{fig:cmd}, we apply an \ewha\ $\ge$ 6\AA cut on galaxy spectra extracted from a 1.0~\reff\ aperture to ensure that all retired galaxies are removed from the sample \citep{Cid-Fernandes:2011}.

@@

Broad-line AGN comprise $\sim$0.9\% of MaNGA's galaxy sample where \citet{Lacerda:2020} found a fraction of $\sim$2.8\% from the CALIFA survey and \citet{Sanchez:2018} found a fraction of $\sim$1.33\% from the MaNGA's MPL-5 sample (which observed $\sim$2700 galaxies).

Among the 6142 MaNGA IFUs considered here, 404 cover close galaxy pairs and multiples. The sample includes 327 pairs, 67 triplets, 7 quadruplets, and 1 quintuplet. Table\,\ref{tab:sample} lists the coordinates and redshifts of these galaxy components in pairs/multiples. When a MaNGA target has multiple companions galaxies, we chose the closest companion to define the pair's mass ratio and projected separation.

For this study, we further restrict the sample by setting a relative velocity cut of $\Delta v$ $<$ 500 km s$^{-1}$. Given the redshift range of the MaNGA sample and the size of MaNGA's IFUs, the maximum projected separation for a companion galaxy in the IFU is $\sim$40 kpc. Again, the galaxy sample is also restricted to galaxies with a stellar mass range of \logm\ $=$ 9.0$-$11.5 and galaxies in the Primary or Secondary MaNGA subsamples. We also require that the galaxies are classified as star forming as described in \S~\ref{sec:data}. These requirements reduce our sample down to 54 star forming MaNGA targets with inside-IFU companions. While we use the identified companions to select galaxy pairs, we only build radial profiles for the MaNGA target galaxies. We do this because the identified companions are not included in the NSA catalog which we use to build the radial profiles for the galaxies.

@@

To show how the population of galaxy pairs differs from isolated galaxies, we will compare our pair sample to a sample of control galaxies in the MaNGA survey. We build this control sample from the MaNGA target galaxies which have no spectroscopic companions within $r_{\rm p}$ $<$ 50 kpc and $\Delta v$ $<$ 500 km s$^{-1}$ either inside or outside of the IFU. This gives us a control sample of 1830 star forming control galaxies.

It has been shown that the SFR in galaxies is dependent on both the stellar mass and the redshift of the galaxies \citep[e.g.,][]{Noeske:2007}. We will compare our interacting galaxies with control galaxies of a similar stellar mass, redshift, and radial size, to account for these other dependencies. To do this, we will use two different methods of pair - control comparison.

@@

In the second method, we select a ``tailored'' control sample for each paired galaxy from the full sample of isolated galaxies. We select a subsample of 20 control galaxies for each paired galaxy. We first select all of the control galaxies which are within 0.1 dex in stellar mass, 0.025 in redshift, 20\% in effective radii, and within the same MaNGA subsample (e.g. Primary or Secondary) as the paired galaxy. With these requirements, most paired galaxies will find between 20$-$60 control galaxies. Since we want each paired galaxy to be treated in a similar manner, we randomly down-select the total number of acquired control galaxies to 20. A given control galaxy may be selected for multiple pairs by the pipeline; most of the control galaxies are used at least once and the average number of times a given control is reused is between 2$-$4 times. In the cases where a paired galaxy does not initially acquire 20 control galaxies we iteratively expand the stellar mass limit by 0.1 dex, the redshift by 0.025, and the \reff\ by 5\% until at least 20 control galaxies are found. 39 pairs required 1 extra iteration, 15 pairs required 2 extra iterations, 5 pairs required 3 extra iterations, and 2 pairs required 4 extra iterations.

@@

\subsection{Specific Star Formation Rate}
We calculate the star formation rates in the pair and control galaxies with the emission lines extracted with our spectra fitting code, {\sc spfit} (described in Section \ref{sec:spfit}). We correct the emission lines for reddening using the extinction curve from \citet{Cardelli:1989} with updated coefficients from \citet{ODonnell:1994}. The extinction is parameterized as $R_V$ $\equiv$ $A_V/E(B-V)$ $=$ 3.1, where we estimate the value of the $V$-band extinction, $A_V$, by comparing the H$\alpha$/H$\beta$ ratio to the expected value of 2.85 for Case-B recombination.

@@

We check our measurement of the specific star formation rate with the equivalent width of the H$\alpha$ line, \ewha, since it is a known proxy for the sSFR. This is useful as the sSFR is dependent on {\sc spfit}'s measurement of the stellar mass while \ewha\ is an observable. As we will show in Section \ref{sec:results}, the radial profiles of \ewha\ is consistent with radial profiles of the sSFR.

The signal to noise ratio of the data will decrease with wide galactocentric radii. MaNGA is designed to cover 1.5 \reff\ for galaxies in the Primary sample and 2.5 \reff\ in the secondary sample. These are not hard limits, data will exist beyond these radii, especially along the semi-minor axis of galaxy; however, the data beyond these limits may be unreliable due to low signal to noise. To control the quality of the used data, we only use spaxels with S/N $\ge$ 3 for the H$\alpha$ line. We also restrict the used spaxels to those with \ewha\ $\ge$ 6 \AA\ to remove retired regions from the survey \citep{Cid-Fernandes:2011}, which effectively sets -10.8 yr$^{-1}$ as the lower limit to the sSFR in our galaxies.

@@

We fit the geometry with apertures from both catalogs when available. When using the first method of pair-control comparison, where pairs and controls are grouped into stellar mass bins, we fit the control galaxies with the NSA apertures. When making the comparison with the second method, paired galaxies fitted with the NSA apertures are compared against controls fitted with the NSA apertures and paired galaxies fitted with the \citet{Simard:2011} apertures are compared against controls fitted with the \citet{Simard:2011} apertures. Further, when defining a galaxy's geometry with the \citet{Simard:2011} apertures we also use the masses given in the catalog for the total stellar mass of the galaxy. Note that although we carefully treat the two catalogs separately whenever possible, we find excellent agreement in the geometry parameters of control galaxies in both catalogs.

@@

The MaNGA sample does not have a uniform spatial coverage, 63\% of the sample is designed to cover 1.5 \reff\ (the Primary+ subsample) and 37\% of the sample is designed to cover 2.5 \reff\ (the Secondary subsample). This means that there will be fewer selected spaxels beyond 1.5 \reff\ and the S/N of the selected spaxels will be lower than those within 1.5 \reff. {\bf We decide to still extend our radial profiles out to 2.5 \reff\ to make full use of the MaNGA data; however, we emphasize that the difference in the sampling of the data within 1.5 \reff\ and the data beyond 1.5 \reff\ may create artificial slopes in the data. }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{ssfr_comb.pdf}
\caption[]{The log(sSFR) as a function of galactocentric radius for control galaxies (\textbf{Left}) and galaxy pairs (\textbf{Middle}). The difference between the profiles of the paired galaxies and the control galaxies are shown in the \textbf{Right} panel. The dashed black profile represents the mean of the difference profiles. The colors of the profiles represent the mass range of the selected galaxies which is given in the legend along with the number of galaxies in that mass bin in parantheses. The highlighted region around the profiles represent the standard error of the mean of the data at the given radius interval. {\bf The vertical dash-dot line marks 1.5 \reff, beyond which the radial sampling is expected to fall.}}
\label{fig:ssfr_prof}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In the first method, paired and control galaxies are grouped into five evenly spaced stellar mass bins between \logm\ $=$ 9.0$-$11.5. Within each stellar mass bin, we create a median profile of log(sSFR) as a function of \reff-scaled galactocentric distance for both paired and control galaxies. The control profiles are constructed using all available control galaxies within each mass bin. The error associated with the ``stacked'' profile is the standard error of mean of the data at each radius bin. Here we define the standard error of the mean, $\sigma_{\overline{x}}$, as,
\begin{equation}
\sigma_{\overline{x}} = \frac{\sigma}{\sqrt{n}},
\end{equation}
where $\sigma$ is the standard deviation and $n$ is the sample size.

@@

We repeat this analysis for the \ewha\ in Figure \ref{fig:ewha_prof}. We find that the \ewha\ profiles are in close agreement with the sSFR profiles, which shows that we can be confident of {\sc spfit}'s measurement of the sSFR. We do see that the pair-control offsets are lightly suppressed using the \ewha\ as the $\Delta$log(\ewha) is only enhanced by 0.25 dex where the $\Delta$log(sSFR) was enhanced by 0.30 dex.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=0.8\linewidth]{ssfr_mass.pdf}
\caption[]{The \textbf{Left} panel shows the $\Delta$log(sSFR) profiles where the difference profiles are constructed from the difference between the paired galaxy profiles and a set of 20 control galaxies. The profiles are split into five different stellar mass bins and the highlighted region about the profiles represent the standard error of mean of the profile. The black dashed line represents the mean profile between the four difference mass ranges. The number of paired galaxies in each mass range is given in the legend in parentheses. The \textbf{Right} panel shows the nuclear $\Delta$log(sSFR) extracted from a 0.5\reff\ aperture. The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars). The vertical error bars on the black squares represent the standard deviation within the bin. The horizontal, dashed black line represents the median central enhancement of the pair sample. Galaxies in the outside-IFU (Blue) and inside-IFU (Red) samples are separately depicted. {\bf The vertical dash-dot line marks 1.5 \reff, beyond which the radial sampling is expected to fall. }
}
\label{fig:ssfr_mass}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{Tailored-Controls Difference Profiles}\label{sec:tailored}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=0.8\linewidth]{ssfr_dm.pdf}
\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by the mass ratio of the pair. The \textbf{top} row is the absolute value of the mass ratio and the \textbf{bottom} row is the mass ratio without taking the absolute value. Taking the mass ratio without the absolute value allows us to separately study the more massive companions of pairs from the less massive companions from pairs. The inside-IFU sample is left out of this analysis because we do not yet have reliable measurements of their total stellar mass ratios.}
\label{fig:ssfr_dm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the second method, we match each paired galaxy to a set of 20 control galaxies of similar stellar masses and redshifts, as described in \S~\ref{sec:control}. We then take the median of the azimuthally averaged profiles of the tailored control sample. Finally, we obtain the $\Delta\log$sSFR profile for each of the 169 paired galaxies by calculating the difference between its sSFR profile and the median profile of its control sample.

@@

To focus on the sSFR offsets in the centers of the galaxies, we also calculate the sSFR difference between each paired galaxy and its control sample within the central 0.5~\reff. The central sSFR is calculated for each galaxy by taking spaxels within 0.5 \reff\ and whose H$\alpha$ flux has S/N $\ge$ 3 and then taking the median value of sSFR of the selected spaxels. Once this is done we calculate the $\Delta$log(sSFR) using the same method as the $\Delta$log(sSFR) radial profiles are made. The central sSFR of a paired galaxy is compared against the sSFR of a set of 20 similar control galaxies, the same set of controls which were used for the $\Delta$log(sSFR) profiles, by taking the difference between the central sSFR of the paired galaxy and the median sSFR of the 20 selected control galaxies. We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}.

@@

The central enhancement to the sSFR falls to zero around 1.2 \reff\ and the outskirts of the galaxies are lightly suppressed by 0.0$-$0.1 dex. Within individual mass ranges, there are some mass ranges which feature large enhancements to the sSFR at large radii while other mass ranges show a strong suppression to the sSFR. There appears to be no dependence on the stellar mass of the pair but, as we will show in the next section, \S~\ref{sec:dm}, these offsets at large radii may be dependent on the mass ratio between the galaxy pairs.

To understand why the profiles of high mass galaxies behave differently from the rest of the sample in Figures \ref{fig:ssfr_prof}, \ref{fig:ewha_prof}, and \ref{fig:ssfr_mass}, we compare the distribution of the projected separation for the whole sample and for galaxies in the highest mass bin in Figure \ref{fig:sep_hist}. The whole sample has a v-shaped separation distribution. This is the result of the combination of the two different samples, the inside-IFU and outside-IFU samples. The outside-IFU sample should find more pairs at wide projected separations due to the larger volume to find companions in. The separation distribution of the inside-IFU sample is limited by MaNGA's IFU sizes and the sample's redshift distribution; the maximum possible projected separation for a MaNGA target with $z$ $=$ 0.15 and a 127 spaxel IFU is about 40 kpc.
